The problem and promise of scale in multilayer networks

### 2019-12-08 paper/introduction.Rmd
tidy intro

---
title: The problem and promise of scale in multilayer networks
output: 
  github_document:
    toc: true
author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
date: "-- `r Sys.Date()`"
bibliography: ../references/refs.bib
---

@@

# Box 1: Types of spatial variables 
Multilayer networks can incorporate spatial variables to define edges between nodes and to characterize the spatial context of network layers. Edges connect different entities in the same layer or across layers as well as to the same entities across layers. The spatial context of a network layer is defined here as the landscape elements, generally abiotic, that an animal social system exists within. Depending on the type, a multilayer network may include one or both of these types of spatial variables to better understand the complex connections between social systems and the landscapes they

The main types of spatial data that can be included in multilayer networks are georeferenced biologging data and landscape level data. Georeferenced biologging data, including radio-frequency identification tags (RFID), passive
integrated transponder (PIT), radiotelemetry, and Global Positioning System (GPS) devices, provide an alternative to intensive direct observations of individuals and their interactions. In addition, some animals are not easily observed, e.g.: marine mammals and birds, and these data provide an inside look. Some derived products can be generated from these data as well, including home ranges, utilization distributions and habitat patches. Landscape level data include relatively stable measures of a lanscape such as land cover, land use and elevation, and more variable measures such as temperature, precipitation and snow cover.

Given the variety of multilayer networks and types of spatial data that can be included, there are a large number of ways to combine them. Multilayer networks may be composed of categorical and unordered layers (termed 'categorical coupling'), including spatial variables such as land cover, land use, and explicit habitat patches. Multiplex networks, where each layer represents a different type of interaction, may be composed of a layer defined by an association index and another one by home range overlap. A network of networks may be used to represent communities as layers with interlayer edges defined by their spatial connectivity and intralayer edges defined by a spatially derived association index.

<!-- it's complicated -->

Spatial scale influences all of these types of spatial data and the inferences derived when combining them in a multilayer network

All biologging sensors have some spatial error

In addition, biologging sensors vary in terms of fix rate or data collection rate. GPS collars can be programmed but will inevitably vary
Temporal grouping

All remotely sensed imagery is an average of area on land, reported by the

Matching scale of imagery to resolution of fix rate

PIT tags have <1m reading distance [@krause2013]
GPS collars have challenges due to dense vegetation 
Telemetry >10m location error

* how associations are measured: e.g. spatsoc
* how relocations are categorized: e.g. landcover

Multilayer networks incoroprate spatial variables in two ways:

1. for determining association between individuals in a social system
1. for characterizing the spatial context of social systems

## Measuring association
For example, association between individuals can be determined using georeferenced biologging devices such as radio‐frequency identification tags, radiotelemetry, and global positioning system (GPS) devices.

Proximity based social networks (PBSNs) are association networks based on close proximity between individuals [@spiegel2016].

Biologging with GPS allows for simultaneous spatiotemporal sampling of multiple individuals in a group or population

## Spatial context
The spatial context of social systems can be defined as all

what is the spatial context of an animal social system

explicit spatial locations
habitat patches
landscape/habitat connectivity
social variable + home range overlap = opportunity to interact

>>>>

---
output: github_document
bibliography: ../references/refs.bib
---

@@
